Programming Assignment 2

### 2015-04-02 paper.tex

\section{LVQ}
Our LVQ network was created using the Neural Net toolkit for Matlab. We selected a hidden-layer size of [2 * n] to allow the target classes to be created with little room for error in the way of dying centroids based on the order of training. Making use of the built-in training of the toolkit, we simply constructed an input matrix consisting of all of our outlines for each group and made target vectors to use with them. 
\subsection{Image Encoding}
Images were encoded by simply importaing the RGB map, grayscaling, and converting the grayscale 0-255 to -1 and 1 based on a threshold (taken to be 127). These images were also resized to the global size of 64 x 48. The resultant images were those that were thrown into the input matrix and used to train the lvq network.

>>>>

\section{LVQ}
